Contracts for Contracts

### 2023-06-30 paper/formal_model.tex
update syntax, minorly

We can also define interfaces at top-level, which only contain function
declarations. Interfaces are useful when invoking functions on addresses,
providing expected types of arguments and returned values of the address call.

@@

Specifications attached to function definitions first introduce bindings for
the guarded function, including the names for the guarded callee, call options,
ordinary arguments, and returned values. The following snippet shows an example
\[
  \overbrace{\mathit{fp^*}}^{\text{callee}}\Keywd{\{}\underbrace{(x : y)^*}_{\text{call options}}\Keywd{\}(}\overbrace{x^*}^{\text{arguments}}\Keywd{)} ~\Keywd{returns (}\underbrace{y^*}_{\text{returned values}}\Keywd{)}
\]
The precondition and postcondition are denoted in the \code{requires}-clause and
\code{ensures}-clause, respectively.
In practice not all functions need to be specified with conditions.
In such cases, a no-op specification is expressed where the precondition and
postcondition are simply a boolean expression \code{true}.
In the \code{where}-clause, programmers can specify the condition for addresses
appeared as arguments or returned values for the parent call, recursively using
the same syntax.
When the specification is attached to an address, we allow very flexible ways
to specify the callee. For example, if a struct argument contains an address
value that we would like to guard:
\begin{lstlisting}
// x is a struct argument whose field y is an address
... where { x.y.f requires $\mathit{precond}$ ensures $\mathit{postcond}$ }
\end{lstlisting}
we can use the projection syntax to specify
the condition when address \code{x.y} is called on function \code{f}.

>>>>

We can also define interfaces at top-level, which only contain function
declarations. Interfaces are useful when invoking functions on addresses,
providing expected types of arguments and returned values for the address call.

@@

A specification is attached to a target, which is either a function name or
an address (expressed by an access path due to the existence of nested structures).
When specified for addresses, the programmer provides an interface name at the beginning.
In addition, a specification introduces bindings for call options,
ordinary arguments, and returned values. The following snippet shows an example
of function specification
\[
  \overbrace{\mathit{vote}}^{\text{callee}}\Keywd{\{}\underbrace{(x : y)^*}_{\text{call options}}\Keywd{\}(}\overbrace{x^*}^{\text{arguments}}\Keywd{)} ~\Keywd{returns (}\underbrace{y^*}_{\text{returned values}}\Keywd{)}
\]
The precondition and postcondition are denoted in the \code{requires}-clause and
\code{ensures}-clause, respectively.
In practice not all functions need to be specified with conditions.
In such cases, a no-op specification is expressed where the precondition and
postcondition are simply a boolean expression \code{true}.
In the \code{where}-clause, programmers can specify the condition for addresses
appeared as arguments or returned values for the parent call, recursively using
the same syntax.
When the specification is attached to an address, we allow very flexible ways
to specify the callee. For example, if a struct argument contains an address
value that we would like to guard:
\begin{lstlisting}
// x is a struct argument whose field y is an address
... where { x.y.f requires $\mathit{precond}$ ensures $\mathit{postcond}$ }
\end{lstlisting}
we can use the projection syntax to specify
the condition when address \code{x.y} is called on function \code{f}.
